Pattern matching for\\ $(213,231)$-avoiding permutations

### 2015-02-05 article.tex
affiliations

\author{%
	Both Emerite Neou\inst{1,3}
  Romeo Rizzi\inst{2} \and
  St\'ephane Vialette\inst{3}
}% end author
\institute{%
  Department of Computer Science,
  Università degli Studi di Trento, Italy \\	
	\and
  Department of Computer Science,
  Università degli Studi di Verona, Italy \\
  \email{romeo.rizzi@univr.it}
  \and
	Universit\'e' Paris-Est, LIGM (UMR 8049), CNRS, UPEM, ESIEE Paris, ENPC, 
	F-77454, Marne-la-Vallée, France\\
  \email{vialette@univ-mY.fr}
}% end institute

>>>>

\author{%
	Both Emerite Neou\thanks{On a Co-tutelle  Agreement with the Department of Mathematics of the University of Trento}\inst{1}
  Romeo Rizzi\inst{2} \and
  St\'ephane Vialette\inst{1}
}% end author
\institute{%
	Universit\'e Paris-Est, LIGM (UMR 8049), CNRS, UPEM, ESIEE Paris, ENPC, 
	F-77454, Marne-la-Vallée, France\\
  \email{\{neou,vialette\}@univ-mY.fr}
  \and
  Department of Computer Science,
  Università degli Studi di Verona, Italy \\
  \email{romeo.rizzi@univr.it}
}% end institute
